### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edit to uncertainty discussion

In reality, the quantities associated with these input parameters are not fixed values; rather, the model input parameters can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty. Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature). For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power. Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}. More detailed discussion on the propagation of parameter uncertainty in fire models is available in NUREG-1824 Supplement~1~\cite{NUREG_1824_Sup_1}. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.

>>>>

In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty. Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature). For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power. Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}. More detailed discussion on the propagation of parameter uncertainty in fire models is available in NUREG-1824 Supplement~1~\cite{NUREG_1824_Sup_1}. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
